---
title:  |
        | Multi100 Project - Task 03: 
        | Does Warfare Matter? Severity, Duration, and Outcomes of Civil Wars
author: 
  - Danilo Freire[^danilo]
date: \today
abstractspacing: double
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: ../task01/references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: ../task01/template.latex
---

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University
of Lincoln, Lincoln, UK, <dfreire@lincoln.ac.uk>,
<https://danilofreire.github.io>. Replication materials are available
at: <https://github.com/danilofreire/multi100-project>.

# Introduction
\label{sec:intro}

In this third task, I will conduct an additional analysis using the
"Peach Research Institute Oslo (PRIO)" dataset from @balcells2014does. The instructions
were as follows: ""

The replication confirms the authors' main claim, that irregular conflicts tend
to last longer than conventional and symmetric non-conventional (SNC) civil
wars. I use Stata version 15 and R version 4.2.1 to conduct and report the analysis.

# Analysis
\label{sec:analysis}

The code below replicates models 4 reported in Table 01 [@balcells2014does,
1400]. My estimates are identical to those included in the main paper.

First, I install the packages required for the analysis.

```{r packages, message=FALSE, warning=FALSE, echo=TRUE, cache=TRUE}
# Install necessary packages
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)

# List of packages
packages <- c("devtools", "knitr", "rmarkdown")

installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

# Install and load Statamarkdown
devtools::install_github("Hemken/Statamarkdown")
library(Statamarkdown)
```

Then I use [the authors' Stata
script](https://osf.io/js2my/?view_only=5b822a6c354940c5a5127c97d2c588fd) to
create some of the variables included in the models. Then, I run a Weibull
regression to test the claim that irregular civil wars are more likely to last
longer than conventional and non-symmetric civil conflicts. The _z_-statistic
for the variable of interest (`Irregular`) is 2.51 and reaches standard levels
of statistical significance. The variable coefficient is 0.869 (SE = 0.346, 95%
CI = [0.191, 1.545]). The baseline category is conventional civil wars. The
results are available below.

```{stata analysis, error=FALSE, warning=FALSE, echo=TRUE}
// Load the dataset
sysuse ../task01/TR_panelformat_Replication.dta

// Create variable warend
sort id year
gen warend=0
replace warend=1 if year==yrend

// Some months have 31 days, others 30, 29, 28.
gen curyear=mdy(moend,31,yrend) if yrend!=. & year==yrend & moend!=.
format %td curyear
replace curyear=mdy(moend,30,yrend) if yrend!=. & year==yrend & moend!=. & curyear==.
replace curyear=mdy(moend,29,yrend) if yrend!=. & year==yrend & moend!=. & curyear==.
replace curyear=mdy(moend,28,yrend) if yrend!=. & year==yrend & moend!=. & curyear==.
replace curyear=date("3112"+string(year),"DMY") if curyear==.

// Create variable warbegin
gen warbegin=0
sort id year
by id: replace warbegin=1 if _n==1 

// Create variable origyear
gen origyear=.
format %td origyear
replace origyear=mdy(most,1,yrst) if year==yrst & most!=.
replace origyear=mdy(1,1,yrst) if year==yrst & most==.
replace origyear=date("3112"+string(year-1), "DMY") if year!=yrst

// Set data
stset curyear, id(id) failure(warend==1) time0(origyear) origin(time origyear) ///
scale(30.41667)

// Model 04
streg i.technologyrebellion post1990 lmtnest /// 
lpop gdpenl oil ethfrac deml milper Extsupp_gov_bi ///
Extsupp_reb_bi western eeurop asia ssafrica lamerica, ///
d(w) nolog  vce(robust) time 
```

# Session Information
\label{sec:sessionInfo}

```{r session, cache=T}
sessionInfo()
```

\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}
