---
title:  |
        | The Multi100 Project:
        | Task 02
author: 
date: \today
abstractspacing: double
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: yes
    toc_depth: 3
    template: article-template.latex
---

# Introduction
\label{sec:intro}

This Markdown file contains the code used to reanalyse the findings presented
in the paper "The Beheading of Criminal Organizations and the Dynamics of
Violence in Mexico" by @calderon2015beheading. My analyst ID is `9EFM2_2`, and
the paper ID is `Caldero_n_JournConflictRes_2015_Nv99`. The instructions for
this task are: "_Your analysis should produce a single, main result in terms of
statistical families of z-, t-, F-, or X^2^ tests (or their alternative or
non-parametric versions). You should be as inclusive as possible regarding your
sample choice. You should disregard spillover effects in neighbouring
municipalities in your analysis. You should disregard strategic features of the
municipalities in your analysis._" The article files can be accessed
at <https://osf.io/bsv24/?view_only=84df9267c74b482fa3cf2f4dc611ee48>.

As requested, I have focused exclusively on the main results presented in the
paper, the effect of government interventions on violence in treated
municipalities. I have also included Ciudad Juárez, the most violent city in
the dataset ($idunico = 8037$), in the analysis [@calderon2015beheading, 9]. I
have used negative binomials regressions both with and without the weights
provided by the authors. The analyses presented here were conducted using Stata
15 and the `Statamarkdown` package for `R` [@rbase2022].

The findings suggest that removing the leader of a criminal organization can
decrease violence, but only in the weighted sample (model 03). After the
capture, there was a significant impact on both homicides associated with drug
trafficking and the general population for up to six months ($z = 2.47$ and $z
= 2.41$, respectively). However, the effect was not significant in the period
between six and twelve months, as in the original paper. 

# Reanalysis
\label{sec:reanalysis}

Here, I am sharing the code used to reanalyze the results from the paper. The
first model assesses the impact of leadership capture on homicides that are
potentially associated with drug trafficking. The second model examines the
same effect but incorporates the weights estimated by the authors. Both models
feature Ciudad Juárez. The original findings are presented in Table 02 of the
paper [@calderon2015beheading, 18].

To start the analysis, I load the data and install the required packages.

```{r packages, message=FALSE, warning=FALSE, echo=TRUE}
# Install necessary packages
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)

# List of packages
packages <- c("devtools", "knitr", "rmarkdown", "tidyverse")

installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

# Install and load Statamarkdown
devtools::install_github("Hemken/Statamarkdown")
library(Statamarkdown)
```

The first two models are presented below. Results indicate that the unweighted
model did not find a significant effect of leadership captures on homicides
among young males. In contrast, the weighted model showed a significant effect,
but this effect was only significant in the first six months following
leadership capture.

```{stata upper-table02-rep-model01, error=FALSE, warning=FALSE, echo=TRUE, cache=TRUE}
// Load data
sysuse ./replication.data.beheadings.march.15.dta, clear
tsset idunico date
set matsize 11000

// Table 02: Upper Panel

// Model 01

quiet xi: nbreg d_homi_male_15_39 pob_male_15_39 i.date i.idunico lpub_after06 ///
lpub_after612 lpub_after12 lieupub_after06 lieupub_after612 lieupub_after12 ///
if treat_leader==1 & date>=563 & date<=611, vce(cluster idunico)

estimates table, keep(lpub_after06 lpub_after612 lpub_after12 lieupub_after06 ///
lieupub_after612 lieupub_after12) b(%9.3fc) se(%9.3fc) t(%9.3fc) p(%9.3fc) style(columns)
ereturn list
```

```{stata upper-table02-rep-model03, error=FALSE, warning=FALSE, echo=TRUE, cache=TRUE}
// Model 03
sysuse ./replication.data.beheadings.march.15.dta, clear
tsset idunico date
set matsize 11000

quiet xi: nbreg d_homi_male_15_39 pob_male_15_39 i.date i.idunico lpub_after06 ///
lpub_after612 lpub_after12 lieupub_after06 lieupub_after612 lieupub_after12 ///
if date>=563 & date<=611 [iw = weights_treat_lead_dto], vce(cluster idunico)

estimates table, keep(lpub_after06 lpub_after612 lpub_after12 lieupub_after06 ///
lieupub_after612 lieupub_after12) b(%9.3fc) se(%9.3fc) t(%9.3fc) p(%9.3fc) style(columns)
ereturn list
```

The models presented below replicate the lower panel of Table 02 and estimate
the impact of leadership captures on homicides among the general population.
The first model does not include the weights, while the second model does.
Similarly to the previous models, the unweighted model did not show a
statistically significant effect, but the weighted model did. The effect also
vanishes after six months.

```{stata upper-table02-rep-model01a, error=FALSE, warning=FALSE, echo=TRUE, cache=TRUE}
// Table 02: Lower Panel
sysuse ./replication.data.beheadings.march.15.dta, clear
tsset idunico date
set matsize 11000

// Model 01

quiet xi: nbreg d_homi_not_male_15_39 pob_not_male_15_39 i.date i.idunico ///
lpub_after06 lpub_after612 lpub_after12 lieupub_after06 lieupub_after612 ///
lieupub_after12 if treat_leader==1 & date>=563 & date<=611, vce(cluster idunico)

estimates table, keep(lpub_after06 lpub_after612 lpub_after12 lieupub_after06 ///
lieupub_after612 lieupub_after12) b(%9.3fc) se(%9.3fc) t(%9.3fc) p(%9.3fc) style(columns)
ereturn list
```

```{stata upper-table02-rep-model03a, error=FALSE, warning=FALSE, echo=TRUE, cache=TRUE}
// Model 03
sysuse ./replication.data.beheadings.march.15.dta, clear
tsset idunico date
set matsize 11000

quiet xi: nbreg d_homi_not_male_15_39 pob_not_male_15_39 i.date i.idunico ///
lpub_after06 lpub_after612 lpub_after12 lieupub_after06 lieupub_after612 ///
lieupub_after12 if date>=563 & date<=611 [iw = weights_treat_lead_rest], vce(cluster idunico)

estimates table, keep(lpub_after06 lpub_after612 lpub_after12 lieupub_after06 ///
lieupub_after612 lieupub_after12) b(%9.3fc) se(%9.3fc) t(%9.3fc) p(%9.3fc) style(columns)
ereturn list
```

# Session Information
\label{sec:sessionInfo}

```{r session, cache=T}
sessionInfo()
```

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

