---
title:  |
        | The Multi100 Project:
        | Task 01
author: 
date: \today
abstractspacing: double
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: yes
    toc_depth: 3
    template: article-template.latex
---

# Introduction
\label{sec:intro}

This Markdown file contains the code used to replicate the findings presented
in the paper "The Beheading of Criminal Organizations and the Dynamics of
Violence in Mexico" by @calderon2015beheading. My analyst ID is `9EFM2_2`, and
the paper ID is `Caldero_n_JournConflictRes_2015_Nv99`. The claim being
assessed is that "captures or killings of drug cartel leaders have exacerbating
short-term effects on DTO-related violence." The article files can be accessed
at <https://osf.io/bsv24/?view_only=84df9267c74b482fa3cf2f4dc611ee48>.

The replication results support the authors' main claims, as I was able to
replicate Models 01 and 03 in Tables 02 and 03 using the authors' Stata do
files, available at
<https://osf.io/6zkbg?view_only=84df9267c74b482fa3cf2f4dc611ee48>, without
encountering any errors in their scripts. The analyses were conducted using
Stata 15 and the `Statamarkdown` package for `R` [@rbase2022].

# Replication of the Original Analysis
\label{sec:replication}

The code below replicates the results presented in Tables 2 and 3 of the paper
(pages 18-19 and 20-21, respectively). The focus is solely on the impact of
leadership capture on DTO-related violence, thus, only Models 1 and 3 from each
table are replicated. The outcome of the replication aligns with the results
presented in the paper.

Initially, the data are loaded and the necessary packages for the analysis are
installed.

```{r packages, message=FALSE, warning=FALSE, echo=TRUE}
# Install necessary packages
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)

# List of packages
packages <- c("devtools", "knitr", "rmarkdown", "tidyverse")

installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

# Install and load Statamarkdown
devtools::install_github("Hemken/Statamarkdown")
library(Statamarkdown)
```

Subsequently, the regressions are executed using the Stata code provided by the
authors. The results match those presented in the paper. The main variables of
interest are `lpub_after06` and `lpub_after612`, which represent, respectively,
the levels of homicides 1-6 months and 7-12 months after a leader's capture
[@calderon2015beheading, 17].

```{stata upper-table02-models, error=FALSE, warning=FALSE, echo=TRUE, cache=TRUE}
// Load data
sysuse ./replication.data.beheadings.march.15.dta, clear
tsset idunico date
set matsize 11000

// Table 02: Upper Panel

// Model 01
quiet xi: nbreg d_homi_male_15_39 pob_male_15_39 i.date i.idunico lpub_after06 ///
lpub_after612 lpub_after12 lieupub_after06 lieupub_after612 lieupub_after12 ///
if treat_leader==1 & date>=563 & date<=611 &  idunico!=8037, ///
vce(cluster idunico)

estimates table, keep(lpub_after06 lpub_after612 lpub_after12 lieupub_after06 ///
lieupub_after612 lieupub_after12) b(%9.3fc) se(%9.3fc) t(%9.3fc) p(%9.3fc) style(columns)
ereturn list
```

```{stata upper-table02-model03, error=FALSE, warning=FALSE, echo=TRUE, cache=TRUE}
// Model 03
sysuse ./replication.data.beheadings.march.15.dta, clear
tsset idunico date
set matsize 11000

quiet xi: nbreg d_homi_male_15_39 pob_male_15_39 i.date i.idunico lpub_after06 ///
lpub_after612 lpub_after12 lieupub_after06 lieupub_after612 lieupub_after12 ///
if date>=563 & date<=611 & idunico!=8037 [iw = weights_treat_lead_dto], ///
vce(cluster idunico)

estimates table, keep(lpub_after06 lpub_after612 lpub_after12 lieupub_after06 ///
lieupub_after612 lieupub_after12) b(%9.3fc) se(%9.3fc) t(%9.3fc) p(%9.3fc) style(columns)
ereturn list
```

```{stata lower-table02-model01, error=FALSE, warning=FALSE, echo=TRUE, cache=TRUE}
// Table 02: Lower Panel
sysuse ./replication.data.beheadings.march.15.dta, clear
tsset idunico date
set matsize 11000

// Model 01
quiet xi: nbreg d_homi_not_male_15_39 pob_not_male_15_39 i.date i.idunico lpub_after06 ///
lpub_after612 lpub_after12 lieupub_after06 lieupub_after612 lieupub_after12 ///
if treat_leader==1 & date>=563 & date<=611 & idunico!=8037, ///
vce(cluster idunico)

estimates table, keep(lpub_after06 lpub_after612 lpub_after12 lieupub_after06 ///
lieupub_after612 lieupub_after12) b(%9.3fc) se(%9.3fc) t(%9.3fc) p(%9.3fc) style(columns)
ereturn list
```

```{stata lower-table02-model03, error=FALSE, warning=FALSE, echo=TRUE, cache=TRUE}
// Model 03
sysuse ./replication.data.beheadings.march.15.dta, clear
tsset idunico date
set matsize 11000

quiet xi: nbreg d_homi_not_male_15_39 pob_not_male_15_39 i.date i.idunico lpub_after06 ///
lpub_after612 lpub_after12 lieupub_after06 lieupub_after612 lieupub_after12 ///
if date>=563 & date<=611 & idunico!=8037 [iw = weights_treat_lead_rest], ///
vce(cluster idunico)

estimates table, keep(lpub_after06 lpub_after612 lpub_after12 lieupub_after06 ///
lieupub_after612 lieupub_after12) b(%9.3fc) se(%9.3fc) t(%9.3fc) p(%9.3fc) style(columns)
ereturn list
```

\newpage 

# Reanalysis
\label{sec:reanalysis}

In this section, I present a new analysis of the four models previously
discussed, but using a different functional form. I utilize a robust Poisson
regression approach which effectively addresses potential arbitrary
misspecification issues inherent in the Poisson distribution, as [suggested by
Jeff
Wooldridge](https://www.statalist.org/forums/forum/general-stata-discussion/general/1593251-poisson).
While the authors appropriately utilized a negative binomial specification to
address the issue of overdispersion, the test conducted in this section serves
as an additional robustness check.

I utilized the same control variables and weights as the original analysis, as
I deemed them suitable for the research question and would have made the same
choices if I were conducting the analysis with the available data.

```{stata upper-table02-rep-model01, error=FALSE, warning=FALSE, echo=TRUE, cache=TRUE}
// Load data
sysuse ./replication.data.beheadings.march.15.dta, clear
tsset idunico date
set matsize 11000

// Table 02: Upper Panel

// Model 01

quiet xi: poisson d_homi_not_male_15_39 pob_not_male_15_39 i.date i.idunico lpub_after06 ///
lpub_after612 lpub_after12 lieupub_after06 lieupub_after612 lieupub_after12 ///
if date>=563 & date<=611 & idunico!=8037 [iw = weights_treat_lead_rest], ///
vce(cluster idunico)

estimates table, keep(lpub_after06 lpub_after612 lpub_after12 lieupub_after06 ///
lieupub_after612 lieupub_after12) b(%9.3fc) se(%9.3fc) t(%9.3fc) p(%9.3fc) style(columns)
ereturn list
```

```{stata upper-table02-rep-model03, error=FALSE, warning=FALSE, echo=TRUE, cache=TRUE}
// Model 03
sysuse ./replication.data.beheadings.march.15.dta, clear
tsset idunico date
set matsize 11000

quiet xi: poisson d_homi_male_15_39 pob_male_15_39 i.date i.idunico lpub_after06 ///
lpub_after612 lpub_after12 lieupub_after06 lieupub_after612 lieupub_after12 ///
if date>=563 & date<=611 & idunico!=8037 [iw = weights_treat_lead_dto], ///
vce(cluster idunico)

estimates table, keep(lpub_after06 lpub_after612 lpub_after12 lieupub_after06 ///
lieupub_after612 lieupub_after12) b(%9.3fc) se(%9.3fc) t(%9.3fc) p(%9.3fc) style(columns)
ereturn list
```

```{stata lower-table02-rep-model01, error=FALSE, warning=FALSE, echo=TRUE, cache=TRUE}
// Table 02: Lower Panel
sysuse ./replication.data.beheadings.march.15.dta, clear
tsset idunico date
set matsize 11000

// Model 01
quiet xi: poisson d_homi_not_male_15_39 pob_not_male_15_39 i.date i.idunico lpub_after06 ///
lpub_after612 lpub_after12 lieupub_after06 lieupub_after612 lieupub_after12 ///
if treat_leader==1 & date>=563 & date<=611 & idunico!=8037, ///
vce(cluster idunico)

estimates table, keep(lpub_after06 lpub_after612 lpub_after12 lieupub_after06 ///
lieupub_after612 lieupub_after12) b(%9.3fc) se(%9.3fc) t(%9.3fc) p(%9.3fc) style(columns)
ereturn list
```

```{stata lower-table02-rep-model03, error=FALSE, warning=FALSE, echo=TRUE, cache=TRUE}
// Model 03
sysuse ./replication.data.beheadings.march.15.dta, clear
tsset idunico date
set matsize 11000

quiet xi: poisson d_homi_not_male_15_39 pob_not_male_15_39 i.date i.idunico lpub_after06 ///
lpub_after612 lpub_after12 lieupub_after06 lieupub_after612 lieupub_after12 ///
if date>=563 & date<=611 & idunico!=8037 [iw = weights_treat_lead_rest], ///
vce(cluster idunico)

estimates table, keep(lpub_after06 lpub_after612 lpub_after12 lieupub_after06 ///
lieupub_after612 lieupub_after12) b(%9.3fc) se(%9.3fc) t(%9.3fc) p(%9.3fc) style(columns)
ereturn list
```

\newpage 

# Session Information
\label{sec:sessionInfo}

```{r session, cache=T}
sessionInfo()
```

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

